Dynamic Load Balancing for\\Heterogeneous Systems

### 2011-11-29 paper/paper.tex
Added a few more references.

\bibitem{Dagum1998}
L.~Dagum and R.~Menon,
``OpenMP: An industry-standard API for shared-memory programming'', in
\emph{IEEE Computational Science and Engineering} 1998, pp. 46–55.

@@

\bibitem{Jimenez2009}
V.J.~Jiménez, L.~Villanova, I.~Gelado, M.~Gil, G.~Fursin, and N.~Navarro,
``Predictive Runtime Code Scheduling for Heterogeneous Architectures,'' in
\emph{Proceedings of the 4th International Conference on High Performance Embedded Architectures and Compilers}, 2009, pp. 19-33.

>>>>

\bibitem{Daga2011}
M.~Daga, A.M.~Aji, and W.~Feng,
``On the Efficacy of a Fused CPU+GPU Processor (or APU) for Parallel Computing'' in
\emph{Application Accelerators in High-Performance Computing (SAAHPC)}, 2011, pp. 141-149.

\bibitem{Dagum1998}
L.~Dagum and R.~Menon,
``OpenMP: An industry-standard API for shared-memory programming'' in
\emph{IEEE Computational Science and Engineering} 1998, pp. 46–55.

@@

\bibitem{Jablin2011}
J.A.~Jablin, P.~McCormick, and M.~Herlihy,
``Scout: High-Performance Heterogeneous Computing Made Simple'' in
\emph{Parallel and Distributed Processing Workshops and Phd Forum (IPDPSW)}, 2011, pp. 2093-2096.

\bibitem{Jimenez2009}
V.J.~Jiménez, L.~Villanova, I.~Gelado, M.~Gil, G.~Fursin, and N.~Navarro,
``Predictive Runtime Code Scheduling for Heterogeneous Architectures'' in
\emph{Proceedings of the 4th International Conference on High Performance Embedded Architectures and Compilers}, 2009, pp. 19-33.
